\documentclass[a4paper,12pt]{article}

% Encoding and Language
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% Mathematical Packages
\usepackage{amsmath,amsfonts,amssymb}

% Graphics
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}

% Page Geometry
\usepackage{geometry}
\geometry{top=2cm, bottom=2cm, left=2.5cm, right=2.5cm}

% Hyperlinks
\usepackage{hyperref}

% Floating Objects
\usepackage{float}

% Additional Packages
\usepackage{venndiagram}

% Title Settings
\title{Homework Assignment}
\author{Student: \textbf{Your First Name Last Name}}
\date{\today}

\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace*{1cm}

    \Huge
    \textbf{Homework}

    \vspace{0.5cm}
    \LARGE
    Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Rostislav Lokhov}

    \vfill

    \Large
    ANO HE Central university\\
    \vspace{0.3cm}
    \today

\end{titlepage}

% Table of Contents
\tableofcontents
\newpage

% Main Content
\section{1}

\subsection{a}

\textbf{Task 1}

\textbf{a) Read the blog post below. (10 points)}

\begin{quote}
\textbf{Losing motivation to study at uni}\\
I'm turning to this forum as a last option because I'm really struggling with discipline at uni, and I'm hoping to get some helpful advice here.\\
I do like my course, but studying for certain modules has felt like a chore over the past few semesters, and I can't figure out why (changing courses isn't an option for me). I'm studying business, which involves both language and math-heavy modules. Here are a few ways I've tried to improve my discipline and focus, but nothing seems to be sticking:
\begin{itemize}
    \item I gave the Pomodoro technique a shot, but I kept taking way too long breaks, losing track of time completely.
    \item I'm pretty much addicted to my phone, spending hours scrolling Reddit or watching random YouTube videos. I’ve tried apps to block distracting sites, but I end up bypassing them.
    \item I’ve also tried creating both weekly and daily schedules, but I keep thinking I won’t be able to stick to them, especially when unexpected stuff pops up during the day.
    \item I get distracted by the need to reply quickly to messages, even though I’ve tried going “cold turkey” by turning off my phone for a few hours.
\end{itemize}
In short, I always end up procrastinating, then rushing to study last-minute. With exams coming up, I barely understand half the material, and I hate feeling like this. I’d appreciate any tips on how to stay focused and manage my time better.
\end{quote}

\textbf{Note:}
\begin{itemize}
    \item bypass — to avoid something by going around it
    \item go cold turkey — to stop using something you are addicted to abruptly and completely
\end{itemize}

\textbf{Source: Reddit}

\vspace{1cm}

\textbf{Write a reply to this post (about 120-150 words). In your reply, you should:}
\begin{itemize}
    \item Show empathy by acknowledging the person’s difficulties.
    \item Offer practical advice or techniques to help them stay motivated.
    \item Use phrases you learned in class to express support and encouragement.
\end{itemize}

\textbf{Solution:}

\textbf{a) Reply to the Blog Post:}

\begin{quote}
Hola, amigo. I think that there is a solution of this problem if there is not physical health problem, only mental. Here are a few strategies
that might help:
\begin{enumerate}
\item \textbf{Set Small, Achievable Goals:} Break your study sessions into smaller tasks. Completing these can give you a sense of accomplishment and keep you motivated.

\item \textbf{Limit Phone Usage:} Try keeping your phone in another room or using apps that limit screen time more strictly. Sometimes physical distance helps reduce the temptation.

\item \textbf{Establish a Routine:} Create a consistent daily schedule that includes specific study times and breaks. Sticking to a routine can improve your discipline over time.

\item \textbf{Find a Study Group:} Joining a study group can provide accountability and make studying more engaging.

\item \textbf{Reward Yourself:} After completing a study session, treat yourself to something you enjoy. This can reinforce positive study habits.
\end{enumerate}
You can do it, if you really want to solve this situation!

Best of luck!
\end{quote}

\vspace{1cm}

\subsection{b}
\textbf{b) Choose the correct option. (5 points)}

\begin{enumerate}
    \item All the clips \textbf{have been uploaded} to the website.
    \item I can’t use my laptop because \textbf{it’s being repaired}.
    \item The video \textbf{was filmed} in Mexico City.
    \item Were those documents \textbf{sent} by email or by post?
    \item Not many houses \textbf{are being built} at the moment.
    \item Are those toys \textbf{made} by hand?
    \item We \textbf{weren’t employed} by the government until 2018.
    \item That piano \textbf{hasn’t been played} for years.
\end{enumerate}

\vspace{1cm}

\subsection{c}
\textbf{c) Complete the sentences with the correct active or passive form of the verbs in brackets. (5 points)}

\begin{enumerate}
    \item Many students say they \textbf{feel} overwhelmed at the start of the semester, but this issue can \textbf{be managed} by developing a clear study schedule.
    
    \item The email with project deadlines \textbf{has not been sent} yet, but the task instructions already \textbf{have been uploaded} on the course website.
    
    \item In most courses, students \textbf{are encouraged} to work in groups, but individual tasks \textbf{are assigned} at the end of each week.
    
    \item Last semester, students \textbf{prepared} questions in advance for the presentation on data encryption which \textbf{was given} by an expert from the IT industry.
    
    \item The concept of data flow \textbf{was taught} in the previous lesson, and it \textbf{is reviewed} again during the final exam.
    
    \item We \textbf{have not submitted} our group project yet, but the research data \textbf{has already been collected}.
    
    \item At the university, new methods of data communication \textbf{are developed} every year, and students \textbf{are tested on them} as part of their coursework.
    
    \item I \textbf{started} working on my term paper last week, and I \textbf{have found} most of the sources online.
\end{enumerate}

\end{document}
