\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{venndiagram}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}
\usepackage{float}

% Page Parameters
\geometry{top=2cm, bottom=2cm, left=2.5cm, right=2.5cm}
\geometry{a4paper, margin=1in}

% Document Title
\title{Homework Assignment}
\author{Student: Rostislav Lokhov}
\date{\today}

\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace{1cm}

    \Huge
    \textbf{Homework Assignment}

    \vspace{0.5cm}
    \LARGE
    Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Rostislav Lokhov}

    \vfill

    \Large
    ANO VO Central University\\
    \vspace{0.3cm}
    \today

\end{titlepage}

% Table of Contents
\tableofcontents
\newpage

% Main Content
\section{Module Title}

\subsection{Topic}

\subsubsection{Task 1 \hfill 0.5 points}

\textbf{Problem Statement:}

Solve the following exercises related to vocabulary and sentence construction.

\textbf{Solution:}

\section{Vocabulary B2: CU Homework 103 Week 5}

\subsection{Task a: Fill in the gaps with the words given. Change the form where necessary. One word is extra. (5 points)}

Words to use: worth, inherit, owe, can't afford, borrow, lend, earn, invest, cost, waste, charge

\begin{enumerate}
    \item \textbf{owe} \\
    I \textbf{owe} my friend money because I borrowed some last week for lunch.
    
    \item \textbf{waste} \\
    Sam \textbf{wastes} a lot of money buying things he doesn't really need.
    
    \item \textbf{is worth} \\
    A personal financial plan \textbf{is worth} the time it takes to create it.
    
    \item \textbf{owes} \\
    I don't trust her. Jill never pays back the money she \textbf{owes}.
    
    \item \textbf{cost} \\
    The groceries \textbf{cost} more than I expected, so I need to adjust my budget.
    
    \item \textbf{inherited} \\
    Candice \textbf{inherited} some money from her grandparents and invested it in a startup.
    
    \item \textbf{earn} \\
    I \textbf{earn} extra money by taking side-gigs.
    
    \item \textbf{can't afford} \\
    I \textbf{can't afford} to buy a new car, so I drive a second-hand one.
    
    \item \textbf{charge} \\
    They usually \textbf{charge} a small fee for using the ATM at this bank.
    
    \item \textbf{lend} \\
    Can you \textbf{lend} me a thousand rubles until I get paid on Friday?
\end{enumerate}

\subsection{Task b: Paraphrase the phrases in bold with the words from the box. You may add words or change the forms. (5 points)}

Words to use: take a loan, tax, salary, wage, bill, save, insurance, contactless payment, budget, raise

\begin{enumerate}
    \item Many people prefer \textbf{contactless payment} because it is quick and easy to use.
    
    \item This agreement means that the \textbf{wage} is 1000 rubles.
    
    \item Every business has to pay \textbf{tax} to the government.
    
    \item My \textbf{salary} helps me pay for my living expenses and save for the future.
    
    \item I received the \textbf{bill} for my dinner at the restaurant, showing how much I needed to pay.
    
    \item They pay for \textbf{insurance} in case they get sick.
    
    \item She decided to \textbf{take a loan} to buy a car.
    
    \item They created a \textbf{budget} for the month.
    
    \item Her boss gave her a \textbf{raise} for her excellent work.
    
    \item They \textbf{save} money every month for a vacation.
\end{enumerate}

\subsection{Task c: Put the words in order to make sentences. (5 points)}

\begin{enumerate}
    \item \textbf{If I had a larger income, I would save more for my future.}
    
    \item \textbf{If I earned more money, I would travel more.}
    
    \item \textbf{If my finances were less stressed, I would feel less stressed about budgeting.}
    
    \item \textbf{If I have more money, I will invest wisely.}
    
    \item \textbf{If I had financial education, I would make smarter investment choices.}
\end{enumerate}

\subsection{Task d: Voice Message to Alex with Budgeting Tips}
\end{document}
