\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{hyperref}

\geometry{a4paper, margin=1in}

\title{English}
\author{Rostislav Lokhov}
\date{\today}

\begin{document}

\maketitle

\section*{1F Small Talk}

\subsection*{a) Identifying Problems in Small Talk}

Watch the video "Signs You're Bad At Small Talk.mp4" and tick the problems you notice:

\begin{itemize}
    \item \textbf{Awkward Silence} \checkmark
    \item \textbf{Main Character Talks Too Much} \checkmark
    \item \textbf{Main Character Doesn`t Ask Follow-up Questions} \checkmark
    \item \textbf{Interrupting}
    \item \textbf{Inappropriate Topics}
    \item \textbf{Shorten the Dialogue}
    \item \textbf{Change Ned`s Response to "How Was Your Weekend" Question}
    \item \textbf{Add Follow-up Questions} \checkmark
\end{itemize}

\subsection*{b) Improving Ned`s Small Talk Skills}

Below is the improved conversation to help Ned with his small talk skills:

\begin{quote}
\textbf{You:} Hey, good morning, Ned.

\textbf{Ned:} Good morning! How are you today?

\textbf{You:} I'm good, thanks. And you?

\textbf{Ned:} I'm doing well. How was your weekend?

\textbf{You:} It was great! I went to the park. What did you do?

\textbf{Ned:} I stayed home and watched some movies.

\textbf{You:} That sounds nice. What movie did you watch?

\textbf{Ned:} I watched a comedy. It was very funny. Do you like comedies?

\textbf{You:} Yes, I do. Maybe I will watch it too.

\textbf{Ned:} That's good. Have a nice day!

\textbf{You:} You too, Ned. See you later.
\end{quote}

\subsubsection*{Explanation of Improvements}

\begin{itemize}
    \item \textbf{Removed Awkward Silences:} The conversation flows smoothly without long pauses.
    \item \textbf{Balanced Talking:} Both people talk equally, so one person doesn't dominate the conversation.
    \item \textbf{Added Follow-up Questions:} Ned asks about the movie, showing interest.
    \item \textbf{Shortened the Dialogue:} The conversation is shorter and to the point.
    \item \textbf{Changed Ned`s Response:} Ned answers clearly to "How was your weekend?" and adds more details.
\end{itemize}

\end{document}
