\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{English Homework Solutions - Week 6}
\author{Rostislav Lokhov \\ Student, ANO HE Central University}
\date{October 25, 2024}


\newpage

\begin{document}

\maketitle

\section*{a) Comparative Forms}

\begin{enumerate}[label=\arabic*.]
    \item better
    \item more carefully
    \item farther/further
    \item more talented
    \item busier
    \item less
    \item more excited
    \item easier
    \item worse
    \item friendlier
    \item more efficiently
    \item more complex
    \item more secure
    \item faster
    \item more innovative
    \item more reliable
    \item more expensive
    \item more frequently
    \item more powerful
    \item more intelligent
\end{enumerate}

\section*{b) Filled Gaps}

\begin{enumerate}[label=\arabic*.]
    \item The new AI system is \textbf{more intelligent than} its predecessor at solving complex problems.
    
    \item Our latest software update runs \textbf{worse than} on older hardware, which may lead to slower performance and increased frustration for users.
    
    \item Cloud storage solutions are becoming \textbf{more reliable than} on-premise servers.
    
    \item The company aims to hire \textbf{more talented} developers to work on their innovative projects.
    
    \item Modern encryption methods make data transfers \textbf{more secure than} ever before.
    
    \item The new user interface is \textbf{easier to} navigate compared to the old one.
    
    \item With 5G technology, data can be transmitted from \textbf{farther} distances without significant loss.
    
    \item The latest programming languages are \textbf{more complex than} traditional ones, making them more accessible to beginners.
    
    \item The upgraded processors are \textbf{faster than} the previous generation, improving overall system performance.
    
    \item Our team became \textbf{more excited} as they learned more about the potential of machine learning in cybersecurity.
\end{enumerate}

\section*{c) University Rules}

\begin{enumerate}[label=\arabic*.]
    \item \textbf{✓} Students must / have to attend at least 80\% of their classes.
    
    \item \textbf{✓} You shouldn't / don't have to wear a uniform on campus.
    
    \item \textbf{✓} Smoking isn't allowed / mustn't be done anywhere on university grounds.
    
    \item Students \textbf{must} submit assignments by the deadline.
    
    \item You \textbf{have to} pay tuition fees before the semester starts.
    
    \item Library books \textbf{shouldn't} be taken out of the library without checking them out.
    
    \item Students \textbf{mustn’t} use mobile phones during exams.
    
    \item You \textbf{have to} bring your student ID card to all exams.
    
    \item Plagiarism \textbf{mustn't} be committed in any academic work.
    
    \item Students \textbf{don't have to} participate in extracurricular activities, but it's good for their CVs.
\end{enumerate}

\section*{d) Correct Sentences}

\begin{enumerate}[label=\arabic*.]
    \item Students shouldn't to install unauthorized software on university computers.
    
    \item You must backing up your work regularly to avoid losing important files.
    
    \item Have we to bring our own laptops to the computer lab?
    
    \item \textbf{✓} Students must not share their login credentials with anyone else.
    
    \item Should we to submit the online assignment by midnight?
    
    \item We mustn’t using antivirus software on all our devices.
    
    \item \textbf{✓} You don't have to attend the optional coding workshop, but I guess it might be quite useful.
    
    \item Must students create a new password every month?
    
    \item \textbf{✓} The university has to provide free Wi-Fi access everywhere on the campus.
    
    \item \textbf{✓} The IT department should be notified immediately if you suspect a virus on your device.
\end{enumerate}

\end{document}
