\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{hyperref}

\geometry{a4paper, margin=1in}

\title{English}
\author{Rostislav Lokhov}
\date{\today}

\begin{document}

\maketitle

\section*{1E Computer Ethics}

\subsection*{a) Completion with Words/Expressions}

Complete the sentences with a word or expression from the box. Some expressions are used more than once.

\textbf{Box:} \textit{after, as soon as, before, if, unless, until, when}

\begin{enumerate}[label=\textbf{01.}]
    \item \textbf{If} we finish this task, we can go out with our friends.
    \item Let’s wait \textbf{until} we receive feedback from the tutor.
    \item We need this task completed right now so please do it \textbf{as soon as} you can.
    \item Michael won’t get this job \textbf{unless} he continues to argue with the HR.
    \item I’ll send you an email \textbf{as soon as} I finish with the project.
    \item I can’t finish this task \textbf{unless} you help me. It’s incredibly difficult.
    \item Our teacher will definitely praise you \textbf{if} you complete all of the tasks.
    \item I want to keep reading this document \textbf{until} I understand something.
    \item I need to submit some documents \textbf{if} I want to study here.
    \item \textbf{After} you correct this line, try running the program again.
\end{enumerate}

\subsection*{b) Completion with 0 or 1st Conditional}

Complete the sentences using the 0 or 1st conditional forms.

\begin{enumerate}[label=\textbf{01.}]
    \item I’ll text you \textbf{when I get} the note from the tutor.
    \item Don’t forget to turn off your computer \textbf{before you leave}.
    \item Sally \textbf{will not go} to the party until she finishes the task.
    \item If I join this club, I \textbf{will not be able} to spend enough time with you.
    \item When the teacher figures out what the student has done, she \textbf{will be} angry.
    \item If you like science, you \textbf{will enjoy} reading this book.
    \item Molly \textbf{will not take part} in this meeting unless you ask her.
\end{enumerate}

\section*{2. Reading Comprehension}

\subsection*{a) True or False}

Read the statements below based on the provided text and mark them as \textbf{True} or \textbf{False}.

\begin{enumerate}
    \item The text suggests that technology always makes it easier to understand what is morally right or wrong. \hfill \textbf{False}
    \item Big data raises concerns about who should control the data that has been collected. \hfill \textbf{True}
    \item AI decision-making processes are easy for the average person to understand. \hfill \textbf{False}
    \item Including diverse perspectives in AI development could help reduce bias. \hfill \textbf{True}
    \item The text indicates that the safety and privacy of health data are not a concern in digital health. \hfill \textbf{False}
\end{enumerate}

\subsection*{b) Multiple Choice}

Choose the correct option (a, b, or c) for each question based on the text.

\begin{enumerate}[label=\textbf{01.}]
    \item According to the text, what role do individuals have in evaluating new technologies?
    \begin{itemize}
        \item[a)] They need to judge whether the advantages are greater than the disadvantages.
        \item[b)] They should rely on companies to make ethical decisions.
        \item[c)] They don’t have any responsibility in making ethical choices.
    \end{itemize}
    \textbf{Answer: a)} 
    
    \item What concern is highlighted in the text regarding AI?
    \begin{itemize}
        \item[a)] AI consistently offers impartial outcomes.
        \item[b)] AI’s methods of making decisions are difficult for most people to grasp.
        \item[c)] AI is not an important topic in ethical discussions.
    \end{itemize}
    \textbf{Answer: b)} 
    
    \item What action did an American company take in 2018 related to privacy issues?
    \begin{itemize}
        \item[a)] It completely prohibited data collection.
        \item[b)] It removed access for apps that might not have followed privacy rules.
        \item[c)] It gave all apps unrestricted access to user data.
    \end{itemize}
    \textbf{Answer: b)} 
    
    \item What concern does the text raise about the future of digital health?
    \begin{itemize}
        \item[a)] The protection and confidentiality of patient information.
        \item[b)] The requirement for more healthcare facilities.
        \item[c)] The unavailability of digital health technology.
    \end{itemize}
    \textbf{Answer: a)} 
    
    \item According to the text, how can developers help reduce bias in AI?
    \begin{itemize}
        \item[a)] By excluding AI from important decisions.
        \item[b)] By making AI’s design processes more secretive.
        \item[c)] By involving more people with a wider range of views in the development process.
    \end{itemize}
    \textbf{Answer: c)} 
    
    \item What does the text suggest about the future availability of healthcare?
    \begin{itemize}
        \item[a)] Medical care will be limited to certain locations.
        \item[b)] High-quality healthcare will be accessible from anywhere.
        \item[c)] Healthcare services will become less affordable.
    \end{itemize}
    \textbf{Answer: b)}
\end{enumerate}

\end{document}
