\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{venndiagram}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}
\usepackage{float}

% Page Parameters
\geometry{top=2cm, bottom=2cm, left=2.5cm, right=2.5cm}
\geometry{a4paper, margin=1in}

% Document Title
\title{Homework Assignment}
\author{Student: Rostislav Lokhov}
\date{\today}

\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace{1cm}

    \Huge
    \textbf{Homework Assignment}

    \vspace{0.5cm}
    \LARGE
    Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Rostislav Lokhov}

    \vfill

    \Large
    ANO VO Central University\\
    \vspace{0.3cm}
    \today

\end{titlepage}

% Table of Contents
\tableofcontents
\newpage

% Main Content
\section{GitHub Introduction}

\subsection{Task a: Watch the video and answer the questions. (10 points)}

\begin{enumerate}
    \item \textbf{What is the primary purpose of GitHub according to the video?}
    
    GitHub is a platform that helps people solve problems by building software together.
    
    \item \textbf{How does Sam use GitHub?}
    
    Sam uses GitHub to build software that makes tractors more efficient. She works with her team members BJ, Melinda, and Mike on the same project using GitHub.
    
    \item \textbf{What problem with the Harvester L700 does Eddie want to solve?}
    
    Eddie wants to solve the problem of sharing moisture data and improving harvests by farmers using the Harvester L700 tractor.
    
    \item \textbf{Why does Vijay create a branch in the code?}
    
    Vijay creates a branch in the code to safely make changes and experiment without affecting the main software that is running on the tractors.
    
    \item \textbf{How does GitHub help in the process of collaboration among team members?}
    
    GitHub allows team members to review, discuss, and improve each other's code through pull requests. It keeps a record of everyone's contributions and feedback, making collaboration easy even if the team is spread around the world.
\end{enumerate}

\subsection{Task b: Watch the video again and complete the sentences. (10 points)}

\begin{enumerate}
    \item Sam builds the software that helps make tractors more \underline{\hspace{3cm}}, and she does this on GitHub with the help of her \underline{\hspace{3cm}}.
    
    \textbf{Solution:} efficient, team
    
    \item Eddie has a great idea for how farmers might share their data and \underline{\hspace{3cm}} their harvests. So Eddie opens an \underline{\hspace{3cm}} on GitHub.
    
    \textbf{Solution:} improve, issue
    
    \item Sam thinks that Vijay would be the best person to \underline{\hspace{3cm}}.
    
    \textbf{Solution:} start the job
    
    \item To ensure the tractors keep running smoothly while working on new features, Vijay creates a \underline{\hspace{3cm}} of the code, which acts as an \underline{\hspace{3cm}} timeline for his experiments.
    
    \textbf{Solution:} branch, alternate
    
    \item GitHub \underline{\hspace{3cm}} Vijay's changes and saves \underline{\hspace{3cm}} of his progress as he develops the new features.
    
    \textbf{Solution:} tracks, snapshots
    
    \item Vijay opens a \underline{\hspace{3cm}} on GitHub, allowing his teammates to \underline{\hspace{3cm}} and \underline{\hspace{3cm}} the changes.
    
    \textbf{Solution:} pull request, review, discuss
    
    \item Once the team \underline{\hspace{3cm}} on the changes, they can \underline{\hspace{3cm}} the new feature into the main codebase and it becomes available to everyone.
    
    \textbf{Solution:} signs off, merge
\end{enumerate}

\subsection{Task c: Read the text and the outline below. Record your summary and your opinion. (10 points)}

\subsubsection{Summary}

Upgrading open source software can be very challenging. Git helps developers work together without interfering with each other’s code. Git allows them to maintain different versions and see what changes have been made. GitHub is a popular platform for using Git, offering free hosting for public repositories, while alternatives like Bitbucket provide options for private repositories. Git makes identifying and fixing problems easier by tracking changes and allowing developers to compare different versions of the code.

\subsubsection{Opinion}

I agree that Git is highly useful for collaboration and tracking changes in software development. Although learning Git can be difficult initially, tools like GitHub simplify the process. Personally, I find learning new software tools somewhat challenging, but with consistent practice, it becomes more manageable. I have experienced difficulties when upgrading software, and using Git would help in identifying and resolving the issues by tracking the changes that introduced the problems.

\end{document}
