\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{venndiagram}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}
\usepackage{float}

% Page parameters
\geometry{top=2cm,bottom=2cm,left=2.5cm,right=2.5cm}
\geometry{a4paper, margin=1in}

% Title
\title{Homework}
\author{Student: Lokhov Rostislav}
\date{\today}

\begin{document}

% Title page
\begin{titlepage}
    \centering
    \vspace*{1cm}

    \Huge
    \textbf{Homework}

    \vspace{0.5cm}
    \LARGE
    Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Lokhov Rostislav}

    \vfill

    \Large
    ANO HE CU\\
    \vspace{0.3cm}
    \today

\end{titlepage}

% Table of contents
\tableofcontents
\newpage

% Main text
\section{Listening Skills Practice}

\subsection{Task A}
\textbf{Problem Statement:}
\begin{itemize}
    \item[a)] Choose the correct option. 
    \begin{enumerate}
        \item Jane? I think she writes/is writing a letter at the moment.
        \item I work/am working as a back-end developer.
        \item We don’t go/aren’t going to this restaurant really often.
        \item I do my homework/ am doing my homework. I can’t go out with you today.
        \item I read/am reading their posts at least once a week.
        \item He always knows/is knowing when his co-workers are upset about something.
        \item Our students do/are doing quite well at the moment.
        \item How do you spell/are you spelling this?
        \item Many people enjoy/are enjoying spending time on the beach on holiday.
        \item It is a small business. So, all of us do/are doing different jobs.
    \end{enumerate}
\end{itemize}

\textbf{Solution:}

\begin{enumerate}
        \item Jane? I think she is writing a letter at the moment.
        \item I work as a back-end developer.
        \item We don’t go to this restaurant really often.
        \item I  am doing my homework. I can’t go out with you today.
        \item I read their posts at least once a week.
        \item He always knows when his co-workers are upset about something.
        \item Our students are doing quite well at the moment.
        \item How do you spell this?
        \item Many people enjoy spending time on the beach on holiday.
        \item It is a small business. So, all of us do different jobs.
    \end{enumerate}
    
\vspace{1cm}

\subsection{Task B}
\textbf{Problem Statement:}
\begin{itemize}
    \item[a)]  Underline the verbs in the wrong tense and rewrite them correctly
        \begin{enumerate}
            \item I am working in an IT company as a software engineer. Every day I am writing a code and fixing bugs in our projects. Currently my team works hard to meet deadlines and deliver high-quality products
            to our clients. Every month we are also organizing meetings and discussing about new features and
            improvements for our software.
        \end{enumerate}
\end{itemize}

\textbf{Solution:}

\begin{enumerate}
            \item I work in an IT company as a software engineer. Every day I write code and fix bugs in our projects. Currently, my team is working hard to meet deadlines and deliver high-quality products to our clients. Every month, we also organize meetings and discuss new features and improvements for our software. 
\end{enumerate}

\vspace{1cm}

\subsection{Task C}
\textbf{Problem Statement:}
     Respond to the following questions using but now.
    \begin{itemize}
        \item What do you do in your free time?
        \item What do you like to eat?
        \item Where do you usually spend your free time?
        \item Where do you usually travel?
        \item When do you normally do your homework?
    \end{itemize}

\textbf{Solution:}
\begin{enumerate}
    \item What do you do in your free time?
        I used to stay active in my free time, but now I sleep during my free time.

    \item What do you like to eat?
        I used to enjoy a variety of snacks, but now I prefer fruits like citrus.

    \item Where do you usually spend your free time?
        I used to spend my free time outside, but now I usually spend it in bed.

    \item Where do you usually travel?
        I used to travel to various places for leisure, but now I usually travel to the central university.

    \item When do you normally do your homework?
        I used to do my homework in the evenings, but now I do it whenever I have time.
\end{enumerate}
\vspace{1cm}

\end{document}
