\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{venndiagram}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}
\usepackage{float}

% Page parameters
\geometry{top=2cm,bottom=2cm,left=2.5cm,right=2.5cm}
\geometry{a4paper, margin=1in}

% Title
\title{Homework}
\author{Student: Lokhov Rostislav}
\date{\today}

\begin{document}

% Title page
\begin{titlepage}
    \centering
    \vspace*{1cm}

    \Huge
    \textbf{Homework}

    \vspace{0.5cm}
    \LARGE
    Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Lokhov Rostislav}

    \vfill

    \Large
    ANO HE CU\\
    \vspace{0.3cm}
    \today

\end{titlepage}

% Table of contents
\tableofcontents
\newpage

% Main text
\section{Listening Skills Practice}

\subsection{Task A}
\textbf{Problem Statement:}
\begin{itemize}
    \item[a)] Choose the correct option. 
    \begin{enumerate}
        \item I've never worked / never worked for any IT company in my life.
        \item Rachel wants to learn coding, but she hasn't saved / didn’t save enough money for the course yet.
        \item They have charged / charged us too much for our software subscription last month.
        \item Paul didn't inherit / hasn’t inherited any shares from his grandmother when she passed away.
        \item I can't submit the report. I haven't been / didn’t go to the server room yet.
        \item I've never used / never used cloud storage, but I'd like to try it.
        \item How much has your laptop cost / did your laptop cost?
        \item I haven't had / didn't have any spare USB drives, so I couldn't back up the data.
        \item I love your office - how long have you worked / did you work in it?
        \item My friend has a really well-paid job in an IT company. She has earned / earned £45,000 last year
    \end{enumerate}
\end{itemize}

\textbf{Solution:}

\begin{enumerate}
        \item I've never worked for any IT company in my life.
        \item Rachel wants to learn coding, but she hasn't saved enough money for the course yet.
        \item They charged us too much for our software subscription last month.
        \item Paul didn't inherit any shares from his grandmother when she passed away.
        \item I can't submit the report. I haven't been to the server room yet.
        \item I've never used cloud storage, but I'd like to try it.
        \item How much did your laptop cost?
        \item I didn't have any spare USB drives, so I couldn't back up the data.
        \item I love your office - how long have you worked in it?
        \item My friend has a really well-paid job in an IT company. She earned £45,000 last year
    \end{enumerate}
    
\vspace{1cm}

\subsection{Task B}
\textbf{Problem Statement:}
\begin{itemize}
    \item[a)] Re-order the words to write present perfect and past simple questions. Add ever where needed.
        \begin{enumerate}
            \item you / attend / any coding bootcamps? how / affect / your understanding of IT?
            \item you / attend an IT conference? what / conference about?
            \item you / meet a successful it person? who / you / meet? where / it / be?
            \item you / complete / IT projects / in high school? What / be/ they about?
            \item You / pay for any software? Why / you / need it?            
        \end{enumerate}
\end{itemize}

\textbf{Solution:}

\begin{enumerate}
            \item Have you ever attended any coding bootcamps? How did it affect your understanding of IT? I have attended coding bootcamps like Yandex Intern Codebattle and Speedcoding Battle. These helped me improve my programming skills.
            \item Have you ever attended an IT conference? What was the conference about? I went to an IT conference, which was an intern meetup about Yandex's music search algorithm using machine learning. I learned a lot about new technologies there.
            \item Have you ever met a successful IT person? Who did you meet? Where was it? I know many successful people in IT, but I don’t want to mention their names. I know most of them through my good friends.
            \item Have you ever completed IT projects in high school? What were they about? I have many projects from school. One of them, the most important to me, was improving the quality of underwater filming using neural networks. This project helped me develop my technical skills. https://github.com/rl0h4w
            \item Have you ever paid for any software? Why did you need it? I have never paid for software. I use open-source programs for my needs.         
\end{enumerate}

\vspace{1cm}

\subsection{Task C}
\textbf{Problem Statement:}
     Choose a famous IT entrepreneur/person that was not mentioned in the lesson.\\
    Search the internet for:
    \begin{itemize}
        \item Their background (where they are from, their education)
        \item Their career path (where they worked, what their responsibilities were)
        \item Their success story (what they created, why it became popular)
    \end{itemize}

\textbf{Solution:}

Sam Altman is a well-known entrepreneur and investor in the technology world. Born in St. Louis, Missouri, in 1985, he studied computer science at Stanford University but dropped out to focus on his career.

Sam’s career started with Loopt, a location-based social networking app, which he co-founded in 2005. After Loopt was sold, he joined Y Combinator, a famous startup accelerator, where he became president. During his time there, he helped many startups grow into successful companies.

In 2019, Sam became CEO of OpenAI, a company focused on artificial intelligence. Under his leadership, OpenAI developed ChatGPT, which gained worldwide popularity for its advanced AI capabilities.(Thx for good LLMs and respect for GPT-4o Preview)(Bc I think he contributed significantly to the 3rd Industrial Revolution (1st - machines, 2nd - computers, 3rd - AI))


\vspace{1cm}

\end{document}
