\documentclass[a4paper,12pt]{article}

% Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% Math packages
\usepackage{amsmath,amsfonts,amssymb}

% Graphics
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, calc}
\usepackage{pgfplots}

% Page geometry
\usepackage{geometry}
\geometry{top=2cm, bottom=2cm, left=2.5cm, right=2.5cm}

% Hyperlinks
\usepackage{hyperref}

% Floating objects
\usepackage{float}

% Additional packages
\usepackage{venndiagram}

% Title setup
\title{Homework Assignment}
\author{Student: \textbf{Your Name Here}}
\date{\today}

\begin{document}

% Title page
\begin{titlepage}
    \centering
    \vspace*{1cm}

    \Huge
    \textbf{Homework Assignment}

    \vspace{0.5cm}
    \LARGE
    For the Course: \textbf{English}

    \vspace{1.5cm}

    \textbf{Student: Rostislav Lokhov}

    \vfill

    \Large
    ANO HE Central univercity\\
    \vspace{0.3cm}
    \today

\end{titlepage}

% Table of Contents
\tableofcontents
\newpage

% Main Content
\section{Homework Assignment}

\subsection{Task 1: Vocabulary}
\textbf{Problem Statement:}

Choose the correct option.

\begin{enumerate}
    \item To improve security, it is important to \underline{eliminate} weak passwords. \textbf{Answer: A. eliminate}
    \item We need to \underline{configure} the settings on the device for better performance. \textbf{Answer: C. configure}
    \item The new software update will \underline{facilitate} faster performance. \textbf{Answer: B. facilitate}
    \item It is crucial to \underline{eliminate} the risk of data breaches. \textbf{Answer: A. eliminate}
    \item The company has decided to \underline{adopt} a new security policy. \textbf{Answer: B. adopt}
    \item We must add \underline{a layer} of protection to our system. \textbf{Answer: C. a layer}
    \item The goal is to \underline{facilitate} communication between devices. \textbf{Answer: A. facilitate}
    \item To prevent \underline{data tampering}, we need to monitor all transactions closely. \textbf{Answer: B. data tampering}
    \item Regular updates are essential \underline{to ensure} the safety of our information. \textbf{Answer: A. to ensure}
    \item We’re looking for a network with wider \underline{coverage}. \textbf{Answer: B. coverage}
\end{enumerate}

\vspace{1cm}

\subsection{Task 2: Useful Language}
\textbf{Problem Statement:}

Match the sentence halves.

\begin{enumerate}
    \item \textbf{H.} What do you think about implementing a Wi-Fi mesh network for our office?
    \item \textbf{J.} I completely agree with you because it would provide us with strong internet coverage everywhere.
    \item \textbf{E.} That’s a good point. I would add that it can help our team stay connected while working on-site.
    \item \textbf{C.} That’s an interesting idea, but have you considered using cloud-based project management software instead?
    \item \textbf{D.} I see your point, but I think we still need a reliable internet connection first.
    \item \textbf{B.} To sum up, we’ve agreed that both a mesh network and project management software are important solutions.
    \item \textbf{F.} How do you feel about adding a VoIP phone system?
    \item \textbf{I.} I think that’s a good idea! It would also allow us to communicate easily while we’re out in the field.
    \item \textbf{G.} In conclusion, we recommend that a VPN as well to ensure our client data stays secure.
    \item \textbf{A.} Based on what we’ve discussed, I would like to connect a Wi-Fi mesh network, then look into the cloud-based software and VoIP system.
\end{enumerate}

\vspace{1cm}

\subsection{Task 3: Speaking}
\textbf{Problem Statement:}

Formulate and record an audio response. Question: \textit{What can be done to make IoT a more secure technology?}

\textbf{Solution:}

The dark web is an anonymous part of the internet where illegal activities, including cybercrime, are common. IoT devices are prime targets for these criminals because a single breach can compromise entire networks, leading to massive financial losses for companies. Attacks like DDoS, ransomware, and data theft are prevalent. To counter this, organizations are adopting standard security measures, and IoT manufacturers are integrating better security features into their devices. In my opinion, making IoT devices more secure requires stricter global regulations, enhanced encryption methods, and collaboration across industries to establish robust security practices.

\end{document}
